Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-06-18 article-models-tt.tex
reintroduced the empty context

\subsubsection{The empty context and the empty families}
\label{empty}
We introduce an empty context and an family over $\Gamma$ for every context $\Gamma$. 
It has been suggested to only include empty families and not an
empty context because an empty context is not necessary, but we do have several
reasons to include them. Having an empty context requires also rules asserting 
that a context is the same thing as a family over the empty context and this
gives the categorical structure on contexts for free once one has it for 
families. The main ingredients that will be missing from the theory once an
empty context is avoided are weakening by a context and identity morphisms from
a context to itself. Including these by hand also requires to formulate all the
compatibility rules involving weakening once more for the cases of weakening by
a context and identity terms at contexts. We prefer to state these rules once
and only once and including an empty context helps in this respect.

>>>>

\subsubsection{The empty context and the empty families}
\label{empty}
We introduce an empty context and an family over $\Gamma$ for every context $\Gamma$. 
It has been suggested by some to only include empty families and not an
empty context because an empty context is not necessary, but we do have several
reasons to include them. Having an empty context requires also rules asserting 
that a context is the same thing as a family over the empty context and this
gives the categorical structure on contexts for free once one has it for 
families. The main ingredients that will be missing from the theory once an
empty context is avoided are weakening by a context and identity morphisms from
a context to itself. Including these by hand also requires to formulate all the
compatibility rules involving weakening once more for the cases of weakening by
a context and identity terms at contexts. We prefer to state these rules once
and only once and including an empty context helps in this respect.
